---
title: 2018 Russian election fraud
---

# Data import and cleaning

```{r setup}
library(tidyverse)
library(here)
```

## Extract and import data

If data isn't already unzipped, unzip:
```{r}
if(!file.exists(here("data", "2018.txt"))){
  unzip(here("data", "2018.zip"), exdir = here("data"))
}
```

Import 2018:
```{r}
election_2018 <- read_delim(here("data", "2018.txt"), 
  delim = "\t")
```

## Column name translations

| Russian | English |
|---------|---------| 
| Число избирателей, включенных в список избирателей | Number of voters included in the voters list |
| Число избирательных бюллетеней, полученных участковой избирательной комиссией | The number of ballots received by the  precinct election commission |
| Число избирательных бюллетеней, выданных избирателям, проголосовавшим досрочно | The number of ballots issued to voters who  voted early |
| Число избирательных бюллетеней, выданных в помещении для голосования в день голосования | The number of ballots issued in a polling station on election day |
| Число избирательных бюллетеней, выданных вне помещения для голосования в день голосования | The number of ballots issued  outside the polling station on voting day |
| Число погашенных избирательных бюллетеней | Number of canceled ballot papers |
| Число избирательных бюллетеней в переносных ящиках для голосования | The number of ballots in mobile ballot boxes |
| Число бюллетеней в стационарных ящиках для голосования | Number of ballots in stationary ballot boxes |
| Число недействительных избирательных бюллетеней | Number of invalid ballots |
| Число действительных избирательных бюллетеней | Number of valid ballots |
| Число утраченных избирательных бюллетеней | Number of lost ballots |
| Число избирательных бюллетеней, не учтенных при получении | The number of ballots not recorded in the receipt of |
| Бабурин Сергей Николаевич | Baburin Sergey Nikolaevich |
| Грудинин Павел Николаевич | Grudinin Pavel Nikolaevich |
| Жириновский Владимир Вольфович | Zhirinovsky Vladimir Volfovich |
| Путин Владимир Владимирович | Putin Vladimir Vladimirovich |
| Собчак Ксения Анатольевна | Sobchak Ksenia Anatolyevna |
| Сурайкин Максим Александрович | Suraykin Maxim Alexandrovich |
| Титов Борис Юрьевич | Titov Boris Yuryevich |
| Явлинский Григорий Алексеевич | Yavlinsky Grigory Alekseevich |
 
Extract relevant columns and calculate others: 
```{r}
ballot_counts <- election_2018 %>% 
  select(region,
    tik, 
    uik,
    voters = `Число избирателей, включенных в список избирателей`,
    leader = `Путин Владимир Владимирович`,
    ballots_inside = `Число избирательных бюллетеней, выданных в помещении для голосования в день голосования`,
    ballots_outside = `Число избирательных бюллетеней, выданных вне помещения для голосования в день голосования`,
    ballots_early = `Число избирательных бюллетеней, выданных избирателям, проголосовавшим досрочно`,
    invalid = `Число недействительных избирательных бюллетеней`,
    valid = `Число действительных избирательных бюллетеней`) %>% 
  mutate(
    given = ballots_inside + ballots_outside + ballots_early,
    received = invalid + valid,
    turnout_percent = given/voters * 100,
    leader_percent = leader/received * 100
  ) %>% 
  select(turnout_percent, leader_percent, everything())
```

Filter out some polling stations:
```{r}
ok_stations <-
  ballot_counts %>% 
  filter(received > 0, given < voters, voters > 100)
```

Take a peek:
```{r}
ok_stations
```


## Graphical checks

Should match Figure 1 in article:
```{r}
ok_stations %>% 
  ggplot(aes(leader_percent)) +
    geom_freqpoly(binwidth = 0.1, center = 0) +
    labs(x = "% for Putin")

ok_stations %>% 
  ggplot(aes(turnout_percent)) +
    geom_freqpoly(binwidth = 0.1, center = 0) +
    labs(x = "% Turnout")
```


## Save out some clean data 

```{r}
ok_stations %>% 
  write_csv(here("results", "2018_ok_stations.csv")) %>% 
  write_rds(here("results", "2018_ok_stations.rds"))
```


