---
title: 2018 Russian election fraud
---

# Exploring the analysis

```{r setup}
library(tidyverse)
library(here)

clean_data_location <- here("results", "2018_ok_stations.rds")
ok_stations <- read_rds(clean_data_location)
```

## Calculating a test statistic: the number of integer polling stations

The article uses the **number of polling stations that report an integer turnout** as evidence of election fraud.

**Task 1:**  How many polling stations reported an integer turnout in 2018?

Try with a small example first.  Imagine `x` contains these 4 turnouts:
```{r}
(x <- c(85, 85.2, 100*(((0.8 - 0.2) * 2000))/2000, 100*1562/1838))
```

What should the result be?  How can you calculate it with code?
```{r}

```

Then, try it with the actual turnouts in `ok_stations$turnout_percent`
```{r}

```

## Simulating turnouts

**Task 2**: How would you simulate the turnout percentage for a polling station in the absence of fraud?

What distribution would you use?  What would you use for its parameter values?

Simulate a turnout for the first polling station:
```{r}
ok_stations %>% slice(1)
```
